Automated Formal Synthesis of Digital Controllers for State-Space Physical Plants

### 2017-01-25 cav2017/cav2017.tex
revised contributions

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space one. 
  Such representation allows to study the  input-to-state dynamics, while 
  transfer functions represents only input-output relations and cannot be 
  enough to ensure deeper properties, e.g. the safety property.
%
\item We proposes a synthesis of state feedback controllers that ensures 
  safety properties in addition to the already existing stability conditions,
  that is only  possible in state-space representation. 
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound and 
  complete synthesis of state feedback systems considering the various
  errors sources in the implementation of control algorithm and in the
  computational modeling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}

>>>>

\begin{enumerate}
%
\item In this paper we extend the problem of digital control synthesis 
  from a transfer function representation into a state space one. 
  Such a representation allows to study the  input-to-state dynamics, whereas
  transfer functions only represent input-output relations and are not sufficient 
  to ensure deeper properties, e.g. safety.
%
\item We proposes a synthesis of state feedback controllers that,
  in addition to the already existing stability conditions,
  ensures safety properties,
  which is only  possible in the state-space representation. 
%
\item We develop two approaches: the first, naive, one relies on
  explicit unfolding of the system's dynamics up to the completeness
  threshold, whilst the second one is abstraction-based and leverages
  the concepts of abstraction refinement and acceleration to increase 
  speed whilst retaining soundness. Both approaches provide sound
  synthesis of state feedback systems considering the various
  error sources in the implementation of the control algorithm and in the
  computational modelling of plant dynamics.
%
\item We develop a model for different sources quantization and their
  effect on the state space progression, for which we find safe bounds
  that ensure the safety of our controllers in a hybrid
  continuous-digital domain.
%
\end{enumerate}
